---
title: "Iris k-means cluster"
width: 1440
height: 900
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Data Set Information
  iris data set gives the measurements
  in centimeters of the variables sepal length and width and petal length 
  and width, respectively, for 50 flowers from each of 3 species of iris. 
  
## The idea of the project:
  defines an application that will compute k-means clusters of the Iris data, 
  allowing the user which features to use for the clustering and how many clusters to use.
  
## Sample of Data used:
```{r, echo=TRUE}
head(iris)
```

## K-means Cluster:
- K-Means is one of the most popular "clustering" algorithms
- K-means stores $k$ centroids that it uses to define clusters. 
- A point is considered to be in a particular cluster if it is closer to that cluster's centroid than any other centroid.
 
 **you can the the code of project here:**
 
 [https://doaa-elbanna.shinyapps.io/project/]
 
 **The all files on Github repo:**
 [https://github.com/DoaaElbanna/shinyApp]
 

